### 2019-09-20 bp_discussion.tex

\subsection{Impliciations for Workplaces}
Being able to accurately recognize periods of high-stress in knowledge
workers could enable more respectful workplaces. For example, an
ability to sense and predict stress in the moment could help companies
to prevent or de-escalate potentially dangerous situations in the
workplace, e.g. confrontation between co-workers. Building an 
understanding of stress and focus over time and in the moment
could also help create workplaces that are more conducive
to enabling knowledge workers to be more productive. For example,
this information could be used to feed an  
 an awareness dashboard of a team's stress level,
and avoid digital interruptions in high-stress or high-focus periods
similar to previous studies~\cite{zuger2017reducing}.  Building
an understanding of awakeness and focus could also enable the creation
of workplaces that are conducive to workers producing higher-quality
work. For example, if awakeness or focus wans, they might 
be enhanced by adapting lighting in the workplace 
or scheduling breaks to prevent focus loss.

@@

\subsection{Tai Chi Intervention}
As we described early, the second half of the field study data
collection involved an intervention of tai chi. This intervention was
used to keep participants motivated to continue over the long study
period.  To investigate whether the intervention had any effect, we
linked participants tai chi session attendance data with their
self-reported percieved stress levels. Building a linear mixed model, we found that tai chi
attendance contributed a small amount to decreased stress in the work
week immediately following the tai chi session (slope of -0.188, p <
0.05). However, we did not find a connection between attendance and
stress on the day of the session suggesting that tai chi might have
long-term effects, but is not conducive at relieving stress close
in time to the intervention.

%% %\vspace{0.05in}
%% \noindent
%% \textbf{Ground Truth and Self-Reporting:} 
\subsection{Ground Truth and Self-Reporting}
Studying mental states, such as stress, awakeness and focus,
requires collecting a valid ground truth from each participant.
We spent considerable time when designing the study
 determining the exact questions to ask of participants,
consulting experts in the area, and basing
the questions and wording on previous research and studies. 
Despite the care taken, it is possible that the 
gathered data lacks reliability and validity. Some have
questioned the
reliability and validity of self-reports as we used in our study
due to subjective biases, lack of care in reporting, and the
highly individual nature of reporting aspects such as
stress~\cite{Hernandez11,Hovsepian15}. In addition, in contexts such
as the workplace, as in our study,
participants  might be afraid to genuinely report levels
of aspects, such as sleepiness. Hence, there is a chance that the
self-reports we gatheered  do not adequately reflect the ground
truth of the underlying variables under investigation. It could even be
the case that certain biometrics might represent a more accurate
ground truth of the studied phenomena than the self-reports. This
suggests that a more confirmative study rather than an inquiry study
could be a better approach, and we will explore such routes in future
work.

@@

\subsection{Predicting Stress with Computer Interaction Data}
Knowledge workers, a focus of our work and study, often spend
a large amount of time each day interacting with information on 
their computer at work. An interesting direction for future study
is to consider whether this computer interaction data, which can
be gathered non-invasively as work occurs, could serve to sense
and predict stress, focus and awakeness. Features that could be
investigated include keystrokes per minute, mouse clicks per minute
and changes in the active title window.

>>>>

\subsection{Implications for Workplaces}
Being able to accurately recognize periods of high-stress in knowledge
workers could enable more respectful workplaces. For example, an
ability to sense and predict stress in the moment could help companies
to prevent or de-escalate potentially dangerous situations in the
workplace, e.g. confrontation between co-workers. Building an 
understanding of stress and focus over time and in the moment
could also help create workplaces that are more conducive
to enabling knowledge workers to be more productive. For example,
this information could be used to feed an awareness dashboard of a team's stress level,
and avoid digital interruptions in high-stress or high-focus periods
similar to previous studies~\cite{zuger2017reducing}.  Building
an understanding of awakeness and focus could also enable the creation
of workplaces that are conducive to workers producing higher-quality
work. For example, if awakeness or focus decreases, they might 
be enhanced by adapting lighting in the workplace 
or scheduling breaks to prevent focus loss.

@@

\subsection{The Effect of Tai Chi on Stress}
As described in our study procedure, we offered and asked participants to attend a one-hour Tai Chi class per week for the last four weeks of the study. We recorded each participant's attendance, including which day they attended the offered classes. The two primary reasons for this intervention was to keep participants motivated to continue the self-reports over the long study period, and to offer a technique that might help reduce stress.

While this was not the focus of our study, we performed a secondary analysis to examine whether the Tai Chi classes had any effect on the participants' stress levels in the work days directly following the Tai Chi session. For this, we build a linear mixed model with the self-reported daily stress level as dependent variables and the participants as random effects. We found that Tai Chi attendance contributed a small amount to decreased stress in the work week immediately following the Tai Chi session (slope of -0.188, p <0.05). However, we did not find a connection between attendance and stress on the day of the session suggesting that Tai Chi might have long-term effects, but is not conducive at relieving stress close in time to the intervention. Overall, the Tai Chi thus had a small impact on the collected data of the second month of the study, which poses a threat to the validity to our observed trends for this period of time. However, since knowledge workers might attend these kinds of classes on their own doing, we believe that this is negligible, and the analysis rather provides a weak indication that this kind of stress intervention might in fact help to reduce stress in the wild.

%% %\vspace{0.05in}
%% \noindent
%% \textbf{Ground Truth and Self-Reporting:} 
\subsection{Ground Truth and Self-Reporting}
Studying mental states, such as stress, awakeness and focus,
requires collecting a valid ground truth from each participant.
We spent considerable time when designing the study
 determining the exact questions to ask of participants,
consulting experts in the area, and basing
the questions and wording on previous research and studies. 
Despite the care taken, it is possible that the 
gathered data lacks reliability and validity. Some have
questioned the
reliability and validity of self-reports as we used in our study
due to subjective biases, lack of care in reporting, and the
highly individual nature of reporting aspects such as
stress~\cite{Hernandez11,Hovsepian15}. In addition, in contexts such
as the workplace, as in our study,
participants  might be afraid to genuinely report levels
of aspects, such as sleepiness. Hence, there is a chance that the
self-reports we gathered  do not adequately reflect the ground
truth of the underlying variables under investigation. It could even be
the case that certain biometrics might represent a more accurate
ground truth of the studied phenomena than the self-reports. This
suggests that a more confirmative study rather than an inquiry study
could be a better approach, and we will explore such routes in future
work.

@@

\subsection{Predicting Stress with Computer Interaction Data}
Knowledge workers, a focus of our work and study, often spend
a large amount of time each day interacting with information on 
their computer at work. An interesting direction for future study
is to consider whether this computer interaction data, which can
be gathered non-invasively as work occurs, could serve to sense
and predict stress, focus and awakeness. Features that could be
investigated include keystrokes per minute, mouse clicks per minute
and changes in the active window title.
